Visual inference for networks

### 2016-02-11 paper/network-inference.Rnw
references added

@@

Possible section outline for paper:
\begin{enumerate}
\item Introduction - visual inference, networks
\item Data and Model fitting \& simulation
\item Lineup methods
\item Results
\item Conclusions and Discussion
\end{enumerate}

\section{Examples \st{??}}

\st{
One of the data sets provided with RSiena is a subset of 50 female respondents from the \emph{Teenage Friends and Lifestyle Study} XXX citation??? from \url{https://www.stats.ox.ac.uk/~snijders/siena/s50_data.htm} XXX. There are three friendship networks provided at three timepoints representing the relationships between the 50 teenage girls in the data. There are also actor-level variables observed at each time period, such as a girl's drinking and smoking behavior. These networks are shown in Figure~\ref{fig:friendship_waves}.

@@

The ``data" model is facet \Sexpr{small_lu$group[1]}.

Notice the caption at the top of Table~\ref{vis_accept}.

\begin{table}
%% Table captions on top in journal version
 \caption{SciVis Paper Acceptance Rate: 1994-2006}
 \label{vis_accept}
 \scriptsize
 \begin{center}
   \begin{tabular}{cccc}
     Year & Submitted & Accepted & Accepted (\%)\\
   \hline
     2004 & 167 & 46 & 27.6\\
     2005 & 268 & 88 & 32.8\\
     2006 & 228 & 63 & 27.6
   \end{tabular}
 \end{center}
\end{table}

@@

Citing happens only with cite - like this for the lineup protocol~\cite{buja:2009}, and for RSiena~\cite{RSiena}. Footnotes are ok%
\footnote{Footnotes appear at the bottom of the column}.

>>>>

References for the intro: lineup protocol~\cite{buja:2009}, RSiena~\cite{RSiena}.

@@

Possible section outline for paper: \hh{XXX the  outline looks good XXX }
\begin{enumerate}
\item Introduction - visual inference, networks
\item Data and Model fitting \& simulation
\item Lineup methods \hh{XXX what do you mean by `methods' here? Do you mean the Experimental Design?}
\item Results
\item Conclusions and Discussion
\end{enumerate}

\section{Examples \st{??} \hh{this might be able to go into the data and model fitting section. We need both a theoretical bit on the models (at the beginning of the section), and then a discussion of the examples used in the paper. }}

\st{
One of the data sets provided with RSiena is a subset of 50 female respondents from the \emph{Teenage Friends and Lifestyle Study} \cite{michell:1997, pearson:2000, pearson:2003}. There are three friendship networks provided  \hh{are the networks really provided? I thought RSiena estimated the networks based on the girls' drinking and smoking behaviour?} at three timepoints representing the relationships between the 50 teenage girls in the data. There are also actor-level variables observed at each time period, such as a girls' drinking and smoking behavior. These networks are shown in Figure~\ref{fig:friendship_waves}.

@@

The ``data" model is in panel \#\Sexpr{small_lu$group[1]}.

@@

Footnotes are ok%
\footnote{Footnotes appear at the bottom of the column}.
